A thesis draft

### 2018-11-22 res/sections/08-Background.tex
Add stuff about Network Slice

@@

\subsubsection{Network slicing}
The role of a \emph{network slice} in a 5G architecture is to specifically
handle the Control-plane of a particular service (e.g. smartphones traffic,
autonomous driving, massive IoT), deploying resources in a manner that assure
the required latency, security and reliability. While some very peculiar and
legacy service could require specific hardware, the common resources between
services could be shared in a virtualized way, providing auto-scaling
capabilities in services that are under heavy network pressure.

>>>>

\section{Network slicing}
Internet Service Providers (ISP) provides networking services to a wide range of
users, that have different necessities between them, and that can require
different kind of characteristics, e.g. a network connectivity in a train has
different networking requirements from the one regarding a company. It is with
these presuppositions that emerges the necessity of service optimization based
on the necessities of the users. To solve this problem in the recent years the
concept of Networks Slice (NS) has been introducted~\cite{alliance20155g}. The
NS aims to logically separate this set of services that present different
use-cases, and to achieve this it expoits the SDN and Network Function Chaining
(NFC) that allows network softwarization~\cite{ordonez2017network}.

Even if the first idea of NS goes back to 2002~\cite{peterson2003blueprint}, NSs
ancestor can be found in VLANs, that allows different hosts with no physical
connectivity to be in the same network. The NS concept has attracted a lot of
interest escpecially from the Industries, that is trying to introduce them in
the next mobile network standard, the 5G. More details are provided in
Section~\ref{chap:background:sec:5g:sub:ns}.

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.2]{networkslicing}
  \caption[The three layers model of network slicing]{The three layers model of
    network slicing~\cite{alliance2016description}}
  \label{chap:background:img:network_slicing}
\end{figure}

As is possible to see from the Figure~\ref{chap:background:img:network_slicing},
a network slice is divided in multiple layers, namely the Service Istance Layer,
the Network Slice Instance Layer and the Resource Layer.

\subsection{Service Instance Layer}
The first layer we presented, the \emph{Service Instance Layer}, represents the
business or user services supported. These services are achieved thanks to the
Network Functions (NF)~\cite{kotulski2017end}.

\subsection{Network Slice Instance Layer}
Instead, the \emph{Network Slice Instance Layer} as is possible to see it
contains multiple sub-network instances, tahtn can be virtualized or
non-virtualized.

\paragraph*{Network Functions}
The concept behind NF is to usually elaborate incoming data and forward it to
destination. NF can be physical of virtualized: in the first case is commonly a
set of harware, in the second case instead it can be a software implementation,
decoupled from the hardware where its running.

\vspace{0.5cm}

Every NF should be isolated, so that it only has the possibility to consumed a
defined set of resources.

@@

\subsubsection{Network slicing}
\label{chap:background:sec:5g:sub:ns}
The role of a \emph{network slice} in a 5G architecture is to specifically
handle the Control-plane of a particular service (e.g. smartphones traffic,
autonomous driving, massive IoT), deploying resources in a manner that assure
the required latency, security and reliability. While some very peculiar and
legacy service could require specific hardware, the common resources between
services could be shared in a virtualized way, providing auto-scaling
capabilities in services that are under heavy network pressure.
